Commit Rater

### 2015-08-26 presentations/paper/results.tex
Introduce results
Rename attributor to associator

\TODO{Introduce}

@@

While almost all associator built into Weka provided useful output regarding above criteria, we eventually chose to use the ``Apriori'' attributer\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified. No special parameters are used to call the attributer, only the number of output results has been increased from 10 to 300\footnote{The code to call the attributer can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/runweka\#L9}}. The results have been ordered by confidence of their correctness and can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/samples/sample\_repos.arff.weka}.

>>>>

The following section describes the results of both our repo-level analysis and our machine learning analysis. Selected results are presented and interpreted.

@@

While almost all associator built into Weka provided useful output regarding above criteria, we eventually chose to use the ``Apriori'' associator\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified. No special parameters are used to call the attributer, only the number of output results has been increased from 10 to 300\footnote{The code to call the attributer can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/runweka\#L9}}. The results have been ordered by confidence of their correctness and can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/samples/sample\_repos.arff.weka}.
